Methods paper for erosion

### 2017-09-21 docs/methods/erosion_methods.tex
starting to work on numerical methods section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary Integral Equation Formulation} 
\label{sec:bies}
Here we focus on solving the incompressible Stokes equations with
Dirichlet boundary conditions
\begin{alignat*}{3}
  \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
  \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
  \uu &= \ff,  && \xx \in \bd\Omega.
\end{alignat*}
The viscosity $\mu$ sets the time scale, and we will assume that
$\mu=1$.  We start by defining the double-layer potential, which is the
convolution of the stresslet with a function $\eeta:\bd\Omega
\rightarrow \RR^2$,
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
    \label{eqn:velocityDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the unit outward
normal at $\yy$.  For any density function $\eeta$, the double-layer
potential satisfies the incompressible Stokes equations, but the
double-layer potential can not capture velocity fields corresponding to
rigid body motions~\cite{pow-mir1987}.  A standard method to complete
the double-layer potential is to introduce a Stokeslet and rotlet
centered inside each interior body
\begin{align}
  S[\llambda_k,\cc_k] = \frac{1}{4\pi} \left(-\log \rho \II + 
    \frac{\rr \otimes \rr}{\rho^2} \right)\llambda_k
  \quad \text{and} \quad
  R[\xi_k,\cc_k] = \frac{\rr_k^\perp}{\rho^2}\xi_k,
  \label{eqn:stokeslet_rotlet}
\end{align}
where  $\rr = \xx - \cc_k$, $\cc_k$ is a point inside the $k^{th}$ body,
$\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then, any solution of
the Stokes equations with a Dirichlet boundary condition $\ff$ can be
written as
\begin{align}
  \label{eqn:completed_DLP}
  \uu(\xx) = \DD[\eeta](\xx) + \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
              \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \Omega,
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{subequations}
\label{eqn:completed_BIE}
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DD[\eeta](\xx) + 
      \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \bd\Omega, 
      \label{eqn:DLP}\\
  \llambda_k &= \frac{1}{2\pi}\int_{\gamma_k} \eeta(\yy) \, ds_\yy, 
  \label{eqn:stokeslet} \\
  \xi_k &= \frac{1}{2\pi}\int_{\gamma_k} \yy^\perp \cdot \eeta(\yy)
  \, ds_\yy.
  \label{eqn:rotlet}
\end{align}
\end{subequations}
Finally, because of the incompressibility constraint, the boundary
condition must satisfy 
\begin{align*}
  \int_{\bd\Omega} \ff \cdot \nn \, ds_\yy = 0.
\end{align*}
The result is a rank-one null space of~\eqref{eqn:completed_BIE} which
is removed by adding the rank-one modification 
\begin{align}
  \NN_0[\eeta](\xx) = \int_{\Gamma} 
    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy, \quad \xx \in \Gamma.
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods\label{s:method}} 
We discretize the second-kind integral equation~\eqref{eqn:DLP} using a
Nystr\"om method.  The equations for the
Stokeslets~\eqref{eqn:stokeslet} and rotlets~\eqref{eqn:rotlet} are
approximated with the trapezoid rule.  By applying a quadrature method,
this results in a dense linear system which we solve with fast multipole
accelerated GMRES.  Because of the second-kind nature of the integral
equation, the number of GMRES iterations is mesh independent (but not
geometry independent), and the overall complexity of the Stokes solver
is proportional to the cost of a single matrix-vector multiplication.
The shear stress, pressure, and drag must also be computed using
quadrature, and this can be interpreted as a post-processing step once
the density function, Stokeslets, and rotlets are computed.  All the
quadrature methods are described in Section~\ref{sec:quadrature}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary Integral Equation Formulation} 
\label{sec:bies}
Here we focus on solving the incompressible Stokes equations with
Dirichlet boundary conditions
\begin{alignat*}{3}
  \mu\Delta \uu &= \grad p, \qquad && \xx \in \Omega, \\
  \grad \cdot \uu &= 0,   && \xx \in \Omega, \\
  \uu &= \ff,  && \xx \in \bd\Omega.
\end{alignat*}
The viscosity $\mu$ sets the time scale, and we will assume that
$\mu=1$.  We start by defining the double-layer potential, which is the
convolution of the stresslet with a function $\eeta:\bd\Omega
\rightarrow \RR^2$,
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nn}{\rho^2} \frac{\rr \otimes \rr}{\rho^2} 
    \eeta(\yy) \, ds_\yy, \quad \xx \in \Omega,
    \label{eqn:velocityDLP}
\end{align}
where $\rr = \xx - \yy$, $\rho = \|\rr\|$, and $\nn$ is the unit outward
normal at $\yy$.  For any density function $\eeta$, the double-layer
potential satisfies the incompressible Stokes equations, but the
double-layer potential can not capture velocity fields corresponding to
rigid body motions~\cite{pow-mir1987}.  A standard method to complete
the double-layer potential is to introduce a Stokeslets and rotlets
centered inside each interior body
\begin{align}
  S[\llambda_k,\cc_k] = \frac{1}{4\pi} \left(-\log \rho \II + 
    \frac{\rr \otimes \rr}{\rho^2} \right)\llambda_k
  \quad \text{and} \quad
  R[\xi_k,\cc_k] = \frac{\rr_k^\perp}{\rho^2}\xi_k, 
  \quad k=1,\ldots,M
  \label{eqn:stokeslet_rotlet}
\end{align}
where  $\rr = \xx - \cc_k$, $\cc_k$ is a point inside the $k^{th}$ body,
$\rr^\perp = (r_2,-r_1)$, and $\rho = \|\rr\|$.  Then, any solution of
the Stokes equations with a Dirichlet boundary condition $\ff$ can be
written as
\begin{align}
  \label{eqn:completed_DLP}
  \uu(\xx) = \DD[\eeta](\xx) + \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
              \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \Omega,
\end{align}
where the density function, Stokeslets, and rotlets satisfy
\begin{subequations}
\label{eqn:completed_BIE}
\begin{align}
  \ff(\xx) &= -\frac{1}{2}\eeta(\xx) + \DD[\eeta](\xx) + 
      \sum_{k=1}^{M} S[\llambda_k,\cc_k](\xx) +
      \sum_{k=1}^{M} R[\xi_k,\cc_k](\xx), \quad \xx \in \bd\Omega, 
      \label{eqn:DLP}\\
  \llambda_k &= \frac{1}{2\pi}\int_{\gamma_k} \eeta(\yy) \, ds_\yy, 
  \label{eqn:stokeslet} \\
  \xi_k &= \frac{1}{2\pi}\int_{\gamma_k} \yy^\perp \cdot \eeta(\yy)
  \, ds_\yy.
  \label{eqn:rotlet}
\end{align}
\end{subequations}
Finally, because of the incompressibility constraint, the boundary
condition must satisfy 
\begin{align*}
  \int_{\bd\Omega} \ff \cdot \nn \, ds_\yy = 0.
\end{align*}
The result is a rank-one null space of~\eqref{eqn:completed_BIE} which
is removed by adding the rank-one modification 
\begin{align}
  \NN_0[\eeta](\xx) = \int_{\Gamma} 
    (\nn(\xx) \otimes \nn(\yy))\eeta(\yy) \, ds_\yy, \quad \xx \in \Gamma.
\end{align}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Numerical Methods\label{s:method}} 
There are several 
We discretize the second-kind integral equation~\eqref{eqn:DLP} using a
Nystr\"om method.  The equations for the
Stokeslets~\eqref{eqn:stokeslet} and rotlets~\eqref{eqn:rotlet} are
approximated with the trapezoid rule.  By applying a quadrature method,
this results in a dense linear system which we solve with fast multipole
accelerated GMRES.  Because of the second-kind nature of the integral
equation, the number of GMRES iterations is mesh independent (but not
geometry independent), and the overall complexity of the Stokes solver
is proportional to the cost of a single matrix-vector multiplication.
The shear stress, pressure, and drag must also be computed using
quadrature, and this can be interpreted as a post-processing step once
the density function, Stokeslets, and rotlets are computed.  All the
quadrature methods are described in Section~\ref{sec:quadrature}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spatial Discretization}
\todo[inline]{compute all derivatives in spectral space}
